Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-15 paper.tex
add a bunch of comments

\section{Building Benchmarks}
\label{sec:bench}
\sk{isn't it weird to introduce the built benchmarks without explaining *why* they were chosen? Like, why growing, stable, shrinking is significant regarding garbage collection? same for my 3 benchs, why would I chose those 3 bench strategies?}

@@

We build three benchmarks out of the potential configurations:
\begin{itemize}
\item \emph{FragmentedHeap:} First, objects are allocated one the heap, and some of them are released, leading to a potential memory fragmentation. Then, new objets with a minimum size greater than the new free chunks sizes are allocated.
\item \emph{LargeObjects:} Only large objets with a size greater than 0xFFFF are allocated on the heap.
\item \emph{Data0bjects:} The majority of objects that will be allocated on the heap will be Data objects, which only contains integer of a specific size (in this benchmark, one byte)
\end{itemize}

@@

We evaluated both reference algorithms on the benchmarks built.

@@

\caption{Moose benchmark results piled up.}
\label{MooseRes1}
\end{figure*}

@@

We evaluated the Moose benchmarks using the reference Mark-Compact and Mark-Sweep algorithm and by analysing the wildfly code base\footnote{http://www.wildfly.org/}. The results are shown in Figure \ref{MooseRes1} and \ref{MooseRes2}. In the results, the compaction time includes the time spent in the compact phase in the Mark-Compact and in the sweep phase in the Mark-Sweep. Total full GC time is the total time spent in full GCs, including the compaction time. Scavenge time is the time spent in scavenges, \emph{i.e.,} garbage collection of young objects only. Total execution time is the total execution time, including scavenge and full GC time.

@@

\todo{Sophie}
It would be nice to evaluate both Sweeper and Planning on what we've just discussed.

I think we show exec time, full gc time, scavenge time, compaction time.

>>>>

\section{Building Benchmarks}
\label{sec:bench}
\sk{isn't it weird to introduce the built benchmarks without explaining *why* they were chosen? Like, why growing, stable, shrinking is significant regarding garbage collection? same for my 3 benchs, why would I chose those 3 bench strategies? I know it is kind of explained in the result section but maybe it is a bit late}

@@

We build three benchmarks out of the potential configurations:
\begin{itemize}
\item \emph{FragmentedHeap:} First, objects are allocated one the heap, and some of them are released, leading to a potential memory fragmentation. Then, new objets with a minimum size greater than the new free chunks sizes are allocated.
\item \emph{LargeObjects:} Only large objets with a size greater than 0xFFFF \sk{put real size in Kb here} are allocated on the heap.
\item \emph{Data0bjects:} The majority of objects that will be allocated on the heap will be Data objects, which only contains integer of a specific size (in this benchmark, one byte)
\end{itemize}

@@

We evaluated both reference algorithms on the benchmarks built.
\sk{shouldn't we talk about our set-ups? or maybe not because the 2 benchs were run on different computers ?}

@@

\caption{Moose benchmark results piled up (in ms).}
\label{MooseRes1}
\end{figure*}

@@

\sk{my benchs relies on the same data (the 2 algorithms) + same explanation of the time (full gc and so on). I would move the shared part in the intro of Section 4 and only keep here the part specific to the Moose bench}
We evaluated the Moose benchmarks using the reference Mark-Compact and Mark-Sweep algorithms and by analysing the wildfly code base\footnote{http://www.wildfly.org/}. The results are shown in Figure \ref{MooseRes1} and \ref{MooseRes2}. In the results, the compaction time includes the time spent in the compact phase in the Mark-Compact and in the sweep phase in the Mark-Sweep. Total full GC time is the total time spent in full GCs, including the compaction time. Scavenge time is the time spent in scavenges, \emph{i.e.,} garbage collection of young objects only. Total execution time is the total execution time, including scavenge and full GC time.

@@

We evaluated the configurable benchmarks using the reference Mark-Compact and Mark-Sweep algorithms and by generating specific heap configurations. 
The resulats are shown in Figure \ref{ConfigRes1} and \ref{ConfigRes2}

\paragraph{FragmentedHeap.}
\paragraph{LargeObjects.}
\paragraph{Data0bjects.}
